---
title: "RC_S5_ShockScore"
author: "Anthony Morada"
date: "10/15/2018"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = '~/Documents/GitHub/RC_S5_ShockScore')
setwd("~/Documents/GitHub/RC_S5_ShockScore")

dt <- read.csv("./PressorData.csv")
dt$starttime <- as.POSIXct(strptime(dt$starttime, "%Y-%m-%d %H:%M:%S"))
dt$endtime <- as.POSIXct(strptime(dt$endtime, "%Y-%m-%d %H:%M:%S"))

wt <- read.csv("~/Documents/GitHub/RC_S5_ShockScore/WeightDurations.csv")
# as.numeric(dt$endtime[1] - dt$starttime[1])*60 * dt$phenylrate[1] * 70
```

The values for '_amount' for all drugs seem incorrect, The '_amount' columns for all drugs were recalculated and replaced: '_amount'(mcg) = duration(min) x 'rate'(mcg/kg/min) x weight(first recorded in kg)



From Kals message for Shock Score:  
- Interval = First 12 Hours
- (Amount of Norepinephrine in mic/min + Amount of Epinephrine in mic/min + (MAP-65)*2 + Net fluid balance)/20  + 5 Points for any Dobutamine use + 10 Points for Vasopressin  
  
  


```{r score.v1}


```



